Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex
More Work

@@

@@

We'd like to thank Richard Kreider of the Arlington Public School District for meeting with us to discuss the viability and details of our project when it was in its developing stages and then again to discuss improvements when Kimbee was almost finished.

>>>>

We will now introduce our implementation and solution to the problem posed for children's speech therapy. Before we started designing {\em Kimbee}, we met with speech pathologist Richard Kreider to discuss what features would be needed for a system like this to work \cite{Kreider:Intro}. Mr. Kreider has over 25 years of experience working with children to overcome their speech disorders. Mr. Kreider talked about how this application would need to have a way for children to practice at home as additional work as well as a way for him to track the progress of his students over time. As these were the two most important features Mr. Kreider discussed, we designed Kimbee around them as core features.

\subsection{Game ({\secit Kimbee})}

\subsection{Therapist Portal}

\section{Results}

@@

\section{Future Work}

@@

We would like to thank Richard Kreider of the Arlington Public School District for meeting with us to discuss the viability and details of our project when it was in its developing stages and then again to discuss improvements when Kimbee was almost finished \cite{Kreider:Intro,Kreider:Results}.
